
---
title: "brainImageRdata"
author: "Sara Linker"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteIndexEntry{brainImageRdata}
    %\VignetteEncoding{UTF-8}
theme: lumen
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>"
)
```

BrainImageRdata provides the brainmaps and gene expression data to be used with the companion package brainImager. BrainImageR will internally reference these datasets. They do not need to be accessed by the user directly. 

To load the brainImageRdata datasets into your workspace:

```{r eval = FALSE}
 hub <- ExperimentHub::ExperimentHub()
 a <- list()
    a[1] <- hub[["EH1434"]]
    a[2] <- hub[["EH1435"]]
    a[3] <- hub[["EH1436"]]
    a[4] <- hub[["EH1437"]]
    a[5] <- hub[["EH1438"]]
    a[6] <- hub[["EH1439"]]
    a[7] <- hub[["EH1440"]]
    a[8] <- hub[["EH1441"]]
    a[9] <- hub[["EH1442"]]
    a[10] <- hub[["EH1443"]]
    a[11] <- hub[["EH1444"]]
    a[12] <- hub[["EH1445"]]
    a[13] <- hub[["EH1446"]]
    a[14] <- hub[["EH1447"]]
    a[15] <- hub[["EH1448"]]
    a[16] <- hub[["EH1449"]]
    a[17] <- hub[["EH1450"]]
    a[18] <- hub[["EH1451"]]
```

## brainImageR Experiment Hub Objects:
For a full description of each object please run make-metadata.R. In brief:

**EH1434:** 

  * __Title__: DevHum_low

  * __For use with__: BrainImageR Spatial Analysis (ie: SpatialEnrichment, CreateBrain, PlotBrain)
  
  * __Developmental Timepoint__: Prenatal
  
  * __General Description__: A list of low resolution image masks of the developing human brain. Each element in the list is a different section of the brain. Each matrix within a list element is a segment of the brain to be colored based on enrichment information.

**EH1435:**

  * __Title__: AdHum

  * __For use with__: BrainImageR Spatial Analysis (ie: SpatialEnrichment, CreateBrain, PlotBrain)
  
  * __Developmental Timepoint__: Adult
  
  * __General Description__: A list of low resolution image masks of the adult human brain. Each element in the list is a different section of the brain. Each matrix within a list element is a segment of the brain to be colored based on enrichment information.

**EH1436:**

  * __Title__: Dev_DIM

  * __For use with__: BrainImageR Spatial Analysis (ie: SpatialEnrichment, CreateBrain, PlotBrain)
  
  * __Developmental Timepoint__: prenatal
  
  * __General Description__: A list of the original dimensions of each image mask. Required to reconstruct the image.

**EH1437:**

  * __Title__: ad_DIM

  * __For use with__: BrainImageR Spatial Analysis (ie: SpatialEnrichment, CreateBrain, PlotBrain)
  
  * __Developmental Timepoint__: adult
  
  * __General Description__: A list of the original dimensions of each image mask. Required to reconstruct the image.

**EH1438:** 
  
  * __Title__: dev_abrev

  * __For use with__: BrainImageR Spatial Analysis (ie: SpatialEnrichment, CreateBrain, PlotBrain)
  
  * __Developmental Timepoint__: prenatal
  
  * __General Description__: A list of the tissues in each brain section. Each element in the list corresponds to the same brain sections as in DevHum_low. 

**EH1439:** 
  
  * __Title__: ad_abrev

  * __For use with__: BrainImageR Spatial Analysis (ie: SpatialEnrichment, CreateBrain, PlotBrain)
  
  * __Developmental Timepoint__: adult
  
  * __General Description__: A list of the tissues in each brain section. Each element in the list corresponds to the same brain sections as in AdHum. 

**EH1440:** 
  
  * __Title__: dev_outline

  * __For use with__: BrainImageR Spatial Analysis (ie: SpatialEnrichment, CreateBrain, PlotBrain)
  
  * __Developmental Timepoint__: prenatal
  
  * __General Description__: A list of matrices containing the outline for each brain section. Each element in the list corresponds to the same brain sections as in DevHum_low. 

**EH1441:**

  * __Title__: ad_outline

  * __For use with__: BrainImageR Spatial Analysis (ie: SpatialEnrichment, CreateBrain, PlotBrain)
  
  * __Developmental Timepoint__: adult
  
  * __General Description__: A list of matrices containing the outline for each brain section. Each element in the list corresponds to the same brain sections as in AdHum. 
  
**EH1442:**

  * __Title__: ad_conversion

  * __For use with__: BrainImageR Spatial Analysis (ie: SpatialEnrichment, CreateBrain, PlotBrain)
  
  * __Developmental Timepoint__: adult
  
  * __General Description__: A matrix containing the conversion between microdissected brain regions and the more general brain regions that are plotted in the final heatmap. 
  
**EH1443:**

  * __Title__: dev_slices

  * __For use with__: BrainImageR Spatial Analysis (ie: SpatialEnrichment, CreateBrain, PlotBrain)
  
  * __Developmental Timepoint__: prenatal
  
  * __General Description__: A vector of the different sections available for the prenatal brain 
  
**EH1444:**

  * __Title__: ad_slices

  * __For use with__: BrainImageR Spatial Analysis (ie: SpatialEnrichment, CreateBrain, PlotBrain)
  
  * __Developmental Timepoint__: adult
  
  * __General Description__: A vector of the different sections available for the adult brain

**EH1445:**

  * __Title__: dev_abatissuesBygenes

  * __For use with__: BrainImageR Spatial Analysis (ie: SpatialEnrichment, CreateBrain, PlotBrain)
  
  * __Developmental Timepoint__: prenatal
  
  * __General Description__: Expression information for each microdissected region in the prenatal brain.
  
**EH1446:**

  * __Title__: ad_abatissuesBygenes

  * __For use with__: BrainImageR Spatial Analysis (ie: SpatialEnrichment, CreateBrain, PlotBrain)
  
  * __Developmental Timepoint__: adult
  
  * __General Description__: Expression information for each microdissected region in the adult brain.
  
**EH1447:**

  * __Title__: dev_colmeta

  * __For use with__: BrainImageR Spatial Analysis (ie: SpatialEnrichment, CreateBrain, PlotBrain)
  
  * __Developmental Timepoint__: prenatal
  
  * __General Description__: sample metadata provided by the Allen Brain Institute for the prenatal brain

**EH1448:**

  * __Title__: ad_colmeta

  * __For use with__: BrainImageR Spatial Analysis (ie: SpatialEnrichment, CreateBrain, PlotBrain)
  
  * __Developmental Timepoint__: adult
  
  * __General Description__: sample metadata provided by the Allen Brain Institute for the adult brain

**EH1449:**

  * __Title__: rowmeta

  * __For use with__: BrainImageR Spatial Analysis (ie: SpatialEnrichment, CreateBrain, PlotBrain)
  
  * __Developmental Timepoint__: prenatal and adult
  
  * __General Description__: gene metadata provided by the Allen Brain Institute 
  
**EH1450:**

  * __Title__: alldev_colmeta

  * __For use with__: BrainImageR Temporal Analysis (ie: predict_time). T
  
  * __Developmental Timepoint__: 8 weeks post-conception - 40 years
  
  * __General Description__: sample metadata provided by the Allen Brain Institute

**EH1451:**

  * __Title__: alldev_scale

  * __For use with__: BrainImageR Temporal Analysis (ie: predict_time). 
  
  * __Developmental Timepoint__: 8 weeks post-conception - 40 years
  
  * __General Description__: sample expression data for all timepoints provided by the Allen Brain Institute
